---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ironsworn

<!-- badges: start -->
<!-- badges: end -->

The goal of ironsworn is to provide tools for implementing the ironsworn RPG system in notebook format, including all rolls. 


You can install the development version of this package from [GitHub](https://github.com/Lingtax/ironsworn) with:

``` r
# install.packages("devtools")
devtools::install_github("Lingtax/ironsworn")
```
## Example of use

To be developed later...

```{r example}
library(ironsworn)
set.seed(20190930)
## basic example code
roll_action(1)
oracle_settlement_name()
```

This work is based on Ironsworn (found at www.ironswornrpg.com), created by Shawn Tomkin, and licensed for our use under the Creative Commons Attribution 4.0 International License (https://creativecommons.org/licenses/by/4.0/).